\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-13 manuscript.tex
* Longtables are visible

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{Manuscript.figures/Flowchart1}

@@

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResiduals-1}

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:itmeinfo}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:Testinfo}
\end{figure}

@@

Table \ref{tab:itemfittab} summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by RMSEA value obtained from Signed-\(\chi^2\) index implementation. All of the items had RMSEA value \textless.06 indicating adequate fit. Figure \ref{fig:persornfit} depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (Desjardins \& Bulut, 2018). We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985). Zh \textless{} -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:personfit}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models ((a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:scalechar}
\end{figure}

@@

\begin{appendix}
\section{}
\begin{table}[tbp]

\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}

\begin{tabular}{cccccccc}
\toprule
item & \multicolumn{1}{c}{MR1} & \multicolumn{1}{c}{MR2} & \multicolumn{1}{c}{MR3} & \multicolumn{1}{c}{MR4} & \multicolumn{1}{c}{MR5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
item16 & 1 &  &  &  &  & 0.996 & 0.004\\
item36 & 0.94 &  &  &  &  & 0.897 & 0.103\\
item17 & 0.8 &  &  &  &  & 0.658 & 0.342\\
item11 &  & 0.79 &  &  &  & 0.642 & 0.358\\
item10 &  & 0.76 &  &  &  & 0.592 & 0.408\\
item12 &  & 0.65 &  &  &  & 0.465 & 0.535\\
item7 &  & 0.5 &  &  &  & 0.267 & 0.733\\
item8 &  & -0.49 &  &  &  & 0.252 & 0.748\\
item9 &  & 0.32 &  &  &  & 0.113 & 0.887\\
item27 &  &  & 0.8 &  &  & 0.659 & 0.341\\
item3 &  &  & 0.8 &  &  & 0.683 & 0.317\\
item40 &  &  & 0.65 &  &  & 0.464 & 0.536\\
item30 &  &  & 0.45 &  &  & 0.353 & 0.647\\
item41 &  &  & 0.36 &  &  & 0.329 & 0.671\\
item33 &  &  &  & 0.74 &  & 0.555 & 0.445\\
item32 &  &  &  & 0.73 &  & 0.623 & 0.377\\
item35 &  &  &  & 0.66 &  & 0.455 & 0.545\\
item37 &  &  &  & -0.39 &  & 0.175 & 0.825\\
item38 &  &  &  & 0.38 &  & 0.178 & 0.822\\
item46 &  &  &  &  & 0.6 & 0.422 & 0.578\\
item45 &  &  &  &  & 0.59 & 0.374 & 0.626\\
item25 &  &  &  &  & 0.41 & 0.193 & 0.807\\
item4 &  &  &  &  & 0.41 & 0.219 & 0.781\\
item1 &  &  &  &  & 0.4 & 0.17 & 0.83\\
item26 &  &  &  &  & 0.35 & 0.165 & 0.835\\
\% of Variance & 0.1 & 0.1 & 0.09 & 0.08 & 0.06 &  & \\
\bottomrule
\addlinespace
\end{tabular}

\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}

\begin{tabular}{ccccccccc}
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
item19 & 1.78 &  &  &  &  &  & 3.318 & -2.318\\
item5 &  &  &  &  &  &  & 0.11 & 0.89\\
item16 &  & 1 &  &  &  &  & 1.004 & -0.004\\
item36 &  & 0.91 &  &  &  &  & 0.86 & 0.14\\
item17 &  & 0.81 &  &  &  &  & 0.691 & 0.309\\
item11 &  &  & 0.83 &  &  &  & 0.71 & 0.29\\
item10 &  &  & 0.79 &  &  &  & 0.638 & 0.362\\
item12 &  &  & 0.63 &  &  &  & 0.465 & 0.535\\
item8 &  &  & -0.5 &  &  &  & 0.269 & 0.731\\
item7 &  &  & 0.47 &  &  &  & 0.268 & 0.732\\
item9 &  &  & 0.32 &  &  &  & 0.163 & 0.837\\
item33 &  &  &  & 0.83 &  &  & 0.698 & 0.302\\
item32 &  &  &  & 0.75 &  &  & 0.666 & 0.334\\
item35 &  &  &  & 0.64 &  &  & 0.446 & 0.554\\
item31 &  &  &  & 0.48 &  &  & 0.331 & 0.669\\
item38 &  &  &  & 0.39 &  &  & 0.191 & 0.809\\
item37 &  &  &  & -0.35 &  &  & 0.153 & 0.847\\
item3 &  &  &  &  & 0.85 &  & 0.748 & 0.252\\
item27 &  &  &  &  & 0.8 &  & 0.644 & 0.356\\
item40 &  &  &  &  & 0.68 &  & 0.507 & 0.493\\
item46 &  &  &  &  &  & 0.6 & 0.431 & 0.569\\
item45 &  &  &  &  &  & 0.56 & 0.341 & 0.659\\
item4 &  &  &  &  &  & 0.43 & 0.265 & 0.735\\
item25 &  &  &  &  &  & 0.4 & 0.178 & 0.822\\
item1 &  &  &  &  &  & 0.36 & 0.142 & 0.858\\
item26 &  &  &  &  &  & 0.36 & 0.173 & 0.827\\
item13 &  &  &  &  &  &  & 0.087 & 0.913\\
item29 &  &  &  &  &  &  & 0.108 & 0.892\\
\% of Variance & 0.12 & 0.09 & 0.09 & 0.08 & 0.07 & 0.06 &  & \\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{table}[h]

\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}

\begin{tabular}{ccccccc}
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
Item1 & 2.16 & 1.51 & 0.49 & -0.86 & 0.90* & .21\\
Item2 & 2.76 & 1.75 & -0.10 & -1.42 & 0.88* & .20\\
Item3 & 3.34 & 1.43 & -0.58 & -0.77 & 0.88* & .18\\
Item4 & 1.30 & 1.31 & 1.93 & 2.92 & 0.62* & .32\\
Item5 & 3.95 & 1.56 & -1.42 & 0.75 & 0.70* & .19\\
Item6 & 2.70 & 1.66 & 0.02 & -1.33 & 0.90* & .18\\
Item7 & 2.23 & 1.28 & 0.60 & -0.59 & 0.89* & .18\\
Item8 & 2.95 & 1.24 & -0.19 & -0.70 & 0.93* & -.07\\
Item9 & 2.92 & 1.09 & -0.37 & 0.11 & 0.91* & .14\\
Item10 & 2.73 & 1.07 & -0.03 & -0.52 & 0.92* & .27\\
Item11 & 2.17 & 0.93 & 0.44 & 0.20 & 0.89* & .25\\
Item12 & 2.34 & 1.26 & 0.46 & -0.58 & 0.91* & .24\\
Item13 & 2.71 & 1.49 & 0.14 & -1.29 & 0.89* & .28\\
Item14 & 2.11 & 1.34 & 0.68 & -0.78 & 0.84* & .24\\
Item15 & 3.26 & 1.11 & -0.34 & -0.21 & 0.91* & .11\\
Item16 & 1.46 & 1.31 & 1.71 & 1.90 & 0.65* & .33\\
Item17 & 1.43 & 1.30 & 1.76 & 2.12 & 0.64* & .30\\
Item18 & 0.92 & 0.67 & 2.00 & 9.41 & 0.62* & .32\\
Item19 & 0.85 & 0.56 & 1.71 & 10.74 & 0.55* & .34\\
Item20 & 0.83 & 0.54 & 1.76 & 13.92 & 0.53* & .31\\
Item21 & 0.94 & 0.75 & 2.46 & 10.66 & 0.58* & .27\\
Item22 & 3.57 & 1.08 & -0.72 & 0.08 & 0.88* & .19\\
Item23 & 2.53 & 1.31 & 0.22 & -0.91 & 0.92* & .11\\
Item24 & 4.13 & 1.01 & -1.39 & 2.01 & 0.78* & .19\\
Item25 & 2.57 & 1.43 & 0.22 & -1.23 & 0.88* & .17\\
Item26 & 2.23 & 1.30 & 0.59 & -0.63 & 0.88* & .16\\
Item27 & 3.78 & 1.34 & -1.01 & 0.08 & 0.82* & .18\\
Item28 & 3.75 & 1.16 & -0.78 & -0.10 & 0.86* & .01\\
Item29 & 2.38 & 1.40 & 0.20 & -1.04 & 0.92* & .11\\
Item30 & 0.94 & 1.42 & 1.66 & 1.69 & 0.68* & .24\\
Item31 & 2.91 & 1.76 & -0.24 & -1.41 & 0.87* & .45\\
Item32 & 3.49 & 1.76 & -0.71 & -1.06 & 0.78* & .43\\
Item33 & 3.56 & 1.75 & -0.79 & -0.95 & 0.77* & .32\\
Item34 & 3.30 & 2.00 & -0.54 & -1.50 & 0.74* & .34\\
Item35 & 3.80 & 1.79 & -1.07 & -0.59 & 0.67* & .24\\
Item36 & 1.36 & 1.38 & 1.75 & 2.05 & 0.65* & .38\\
Item37 & 1.30 & 0.94 & 2.79 & 7.65 & 0.48* & -.01\\
Item38 & 4.27 & 1.18 & -2.07 & 4.01 & 0.65* & .23\\
Item39 & 1.94 & 1.01 & 0.85 & 0.61 & 0.86* & .05\\
Item40 & 2.13 & 1.24 & 0.56 & -0.54 & 0.89* & .16\\
Item41 & 0.87 & 1.08 & 1.68 & 2.74 & 0.73* & .21\\
Item42 & 3.90 & 1.55 & -1.15 & -0.12 & 0.72* & .17\\
Item43 & 1.59 & 1.23 & 1.59 & 1.70 & 0.69* & .22\\
Item44 & 3.46 & 1.41 & -0.92 & -0.01 & 0.86* & .38\\
Item45 & 2.04 & 1.66 & 0.46 & -1.12 & 0.87* & .29\\
Item46 & 1.57 & 1.40 & 0.97 & -0.07 & 0.82* & .38\\
Item47 & 2.07 & 1.23 & 0.59 & -0.42 & 0.89* & .34\\
Item48 & 2.57 & 1.30 & 0.14 & -0.74 & 0.93* & .31\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} *p<.001}
\end{tablenotes}

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}

\caption{Correlation plot of the items}\label{fig:figCorAppB}
\end{figure}

{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-1}

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB}
\end{figure}

@@

\begin{longtable}{ccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}\\
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:EFATableAppB} continued}}\\
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
\endhead
item19 & 0.99 &  &  &  &  & 1.007 & -0.007 & 1.058\\
item20 & 0.91 &  &  &  &  & 0.874 & 0.126 & 1.114\\
item18 & 0.82 &  &  &  &  & 0.711 & 0.289 & 1.123\\
item21 & 0.8 &  &  &  &  & 0.683 & 0.317 & 1.163\\
item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.298\\
item11 &  & 0.83 &  &  &  & 0.687 & 0.313 & 1.007\\
item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.031\\
item12 &  & 0.56 &  &  &  & 0.371 & 0.629 & 1.374\\
item8 &  & -0.44 &  &  &  & 0.206 & 0.794 & 1.106\\
item7 &  & 0.42 &  &  &  & 0.226 & 0.774 & 1.614\\
item9 &  & 0.33 &  &  &  & 0.115 & 0.885 & 1.1\\
item16 &  &  & 0.95 &  &  & 0.946 & 0.054 & 1.097\\
item17 &  &  & 0.74 &  &  & 0.595 & 0.405 & 1.168\\
item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347 & 1.431\\
item3 &  &  &  & 0.85 &  & 0.746 & 0.254 & 1.048\\
item27 &  &  &  & 0.78 &  & 0.624 & 0.376 & 1.028\\
item40 &  &  &  & 0.71 &  & 0.512 & 0.488 & 1.05\\
item35 &  &  &  &  & 0.58 & 0.351 & 0.649 & 1.091\\
item48 &  &  &  &  & 0.57 & 0.354 & 0.646 & 1.144\\
item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.085\\
item47 &  &  &  &  & 0.52 & 0.294 & 0.706 & 1.186\\
item44 &  &  &  &  & 0.45 & 0.216 & 0.784 & 1.145\\
item31 &  &  &  &  & 0.41 & 0.206 & 0.794 & 1.477\\
item38 &  &  &  &  & 0.33 & 0.129 & 0.871 & 1.317\\
\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  &  & \\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1}

\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB}
\end{figure}
\end{appendix}

>>>>

{\centering \includegraphics[width=1\linewidth,height=1.5\textheight]{Manuscript.figures/Flowchart1}

@@

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/EFAResiduals-1}

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:itmeinfo}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:Testinfo}
\end{figure}

@@

Table \ref{tab:itemfittab} summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by RMSEA value obtained from Signed-\(\chi^2\) index implementation. All of the items had RMSEA value \textless.06 indicating adequate fit. Figure \ref{fig:personfit} depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (Desjardins \& Bulut, 2018). We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985). Zh \textless{} -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:personfit}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:scalechar}
\end{figure}

@@

\begin{appendix}
\section{}
\begin{center}
\begin{ThreePartTable}

\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}\\
\toprule
item & \multicolumn{1}{c}{MR1} & \multicolumn{1}{c}{MR2} & \multicolumn{1}{c}{MR3} & \multicolumn{1}{c}{MR4} & \multicolumn{1}{c}{MR5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:MinResTab} continued}}\\
\toprule
item & \multicolumn{1}{c}{MR1} & \multicolumn{1}{c}{MR2} & \multicolumn{1}{c}{MR3} & \multicolumn{1}{c}{MR4} & \multicolumn{1}{c}{MR5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
\endhead
item16 & 1 &  &  &  &  & 0.996 & 0.004\\
item36 & 0.94 &  &  &  &  & 0.897 & 0.103\\
item17 & 0.8 &  &  &  &  & 0.658 & 0.342\\
item11 &  & 0.79 &  &  &  & 0.642 & 0.358\\
item10 &  & 0.76 &  &  &  & 0.592 & 0.408\\
item12 &  & 0.65 &  &  &  & 0.465 & 0.535\\
item7 &  & 0.5 &  &  &  & 0.267 & 0.733\\
item8 &  & -0.49 &  &  &  & 0.252 & 0.748\\
item9 &  & 0.32 &  &  &  & 0.113 & 0.887\\
item27 &  &  & 0.8 &  &  & 0.659 & 0.341\\
item3 &  &  & 0.8 &  &  & 0.683 & 0.317\\
item40 &  &  & 0.65 &  &  & 0.464 & 0.536\\
item30 &  &  & 0.45 &  &  & 0.353 & 0.647\\
item41 &  &  & 0.36 &  &  & 0.329 & 0.671\\
item33 &  &  &  & 0.74 &  & 0.555 & 0.445\\
item32 &  &  &  & 0.73 &  & 0.623 & 0.377\\
item35 &  &  &  & 0.66 &  & 0.455 & 0.545\\
item37 &  &  &  & -0.39 &  & 0.175 & 0.825\\
item38 &  &  &  & 0.38 &  & 0.178 & 0.822\\
item46 &  &  &  &  & 0.6 & 0.422 & 0.578\\
item45 &  &  &  &  & 0.59 & 0.374 & 0.626\\
item25 &  &  &  &  & 0.41 & 0.193 & 0.807\\
item4 &  &  &  &  & 0.41 & 0.219 & 0.781\\
item1 &  &  &  &  & 0.4 & 0.17 & 0.83\\
item26 &  &  &  &  & 0.35 & 0.165 & 0.835\\
\% of Variance & 0.1 & 0.1 & 0.09 & 0.08 & 0.06 &  & \\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

\begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}\\
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:sixFacTab} continued}}\\
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
\endhead
item19 & 1.78 &  &  &  &  &  & 3.318 & -2.318\\
item5 &  &  &  &  &  &  & 0.11 & 0.89\\
item16 &  & 1 &  &  &  &  & 1.004 & -0.004\\
item36 &  & 0.91 &  &  &  &  & 0.86 & 0.14\\
item17 &  & 0.81 &  &  &  &  & 0.691 & 0.309\\
item11 &  &  & 0.83 &  &  &  & 0.71 & 0.29\\
item10 &  &  & 0.79 &  &  &  & 0.638 & 0.362\\
item12 &  &  & 0.63 &  &  &  & 0.465 & 0.535\\
item8 &  &  & -0.5 &  &  &  & 0.269 & 0.731\\
item7 &  &  & 0.47 &  &  &  & 0.268 & 0.732\\
item9 &  &  & 0.32 &  &  &  & 0.163 & 0.837\\
item33 &  &  &  & 0.83 &  &  & 0.698 & 0.302\\
item32 &  &  &  & 0.75 &  &  & 0.666 & 0.334\\
item35 &  &  &  & 0.64 &  &  & 0.446 & 0.554\\
item31 &  &  &  & 0.48 &  &  & 0.331 & 0.669\\
item38 &  &  &  & 0.39 &  &  & 0.191 & 0.809\\
item37 &  &  &  & -0.35 &  &  & 0.153 & 0.847\\
item3 &  &  &  &  & 0.85 &  & 0.748 & 0.252\\
item27 &  &  &  &  & 0.8 &  & 0.644 & 0.356\\
item40 &  &  &  &  & 0.68 &  & 0.507 & 0.493\\
item46 &  &  &  &  &  & 0.6 & 0.431 & 0.569\\
item45 &  &  &  &  &  & 0.56 & 0.341 & 0.659\\
item4 &  &  &  &  &  & 0.43 & 0.265 & 0.735\\
item25 &  &  &  &  &  & 0.4 & 0.178 & 0.822\\
item1 &  &  &  &  &  & 0.36 & 0.142 & 0.858\\
item26 &  &  &  &  &  & 0.36 & 0.173 & 0.827\\
item13 &  &  &  &  &  &  & 0.087 & 0.913\\
item29 &  &  &  &  &  &  & 0.108 & 0.892\\
\% of Variance & 0.12 & 0.09 & 0.09 & 0.08 & 0.07 & 0.06 &  & \\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

\begin{longtable}{lllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:tabDesAppB} continued}}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endhead
Item1 & 2.16 & 1.51 & 0.49 & -0.86 & 0.90* & .21\\
Item2 & 2.76 & 1.75 & -0.10 & -1.42 & 0.88* & .20\\
Item3 & 3.34 & 1.43 & -0.58 & -0.77 & 0.88* & .18\\
Item4 & 1.30 & 1.31 & 1.93 & 2.92 & 0.62* & .32\\
Item5 & 3.95 & 1.56 & -1.42 & 0.75 & 0.70* & .19\\
Item6 & 2.70 & 1.66 & 0.02 & -1.33 & 0.90* & .18\\
Item7 & 2.23 & 1.28 & 0.60 & -0.59 & 0.89* & .18\\
Item8 & 2.95 & 1.24 & -0.19 & -0.70 & 0.93* & -.07\\
Item9 & 2.92 & 1.09 & -0.37 & 0.11 & 0.91* & .14\\
Item10 & 2.73 & 1.07 & -0.03 & -0.52 & 0.92* & .27\\
Item11 & 2.17 & 0.93 & 0.44 & 0.20 & 0.89* & .25\\
Item12 & 2.34 & 1.26 & 0.46 & -0.58 & 0.91* & .24\\
Item13 & 2.71 & 1.49 & 0.14 & -1.29 & 0.89* & .28\\
Item14 & 2.11 & 1.34 & 0.68 & -0.78 & 0.84* & .24\\
Item15 & 3.26 & 1.11 & -0.34 & -0.21 & 0.91* & .11\\
Item16 & 1.46 & 1.31 & 1.71 & 1.90 & 0.65* & .33\\
Item17 & 1.43 & 1.30 & 1.76 & 2.12 & 0.64* & .30\\
Item18 & 0.92 & 0.67 & 2.00 & 9.41 & 0.62* & .32\\
Item19 & 0.85 & 0.56 & 1.71 & 10.74 & 0.55* & .34\\
Item20 & 0.83 & 0.54 & 1.76 & 13.92 & 0.53* & .31\\
Item21 & 0.94 & 0.75 & 2.46 & 10.66 & 0.58* & .27\\
Item22 & 3.57 & 1.08 & -0.72 & 0.08 & 0.88* & .19\\
Item23 & 2.53 & 1.31 & 0.22 & -0.91 & 0.92* & .11\\
Item24 & 4.13 & 1.01 & -1.39 & 2.01 & 0.78* & .19\\
Item25 & 2.57 & 1.43 & 0.22 & -1.23 & 0.88* & .17\\
Item26 & 2.23 & 1.30 & 0.59 & -0.63 & 0.88* & .16\\
Item27 & 3.78 & 1.34 & -1.01 & 0.08 & 0.82* & .18\\
Item28 & 3.75 & 1.16 & -0.78 & -0.10 & 0.86* & .01\\
Item29 & 2.38 & 1.40 & 0.20 & -1.04 & 0.92* & .11\\
Item30 & 0.94 & 1.42 & 1.66 & 1.69 & 0.68* & .24\\
Item31 & 2.91 & 1.76 & -0.24 & -1.41 & 0.87* & .45\\
Item32 & 3.49 & 1.76 & -0.71 & -1.06 & 0.78* & .43\\
Item33 & 3.56 & 1.75 & -0.79 & -0.95 & 0.77* & .32\\
Item34 & 3.30 & 2.00 & -0.54 & -1.50 & 0.74* & .34\\
Item35 & 3.80 & 1.79 & -1.07 & -0.59 & 0.67* & .24\\
Item36 & 1.36 & 1.38 & 1.75 & 2.05 & 0.65* & .38\\
Item37 & 1.30 & 0.94 & 2.79 & 7.65 & 0.48* & -.01\\
Item38 & 4.27 & 1.18 & -2.07 & 4.01 & 0.65* & .23\\
Item39 & 1.94 & 1.01 & 0.85 & 0.61 & 0.86* & .05\\
Item40 & 2.13 & 1.24 & 0.56 & -0.54 & 0.89* & .16\\
Item41 & 0.87 & 1.08 & 1.68 & 2.74 & 0.73* & .21\\
Item42 & 3.90 & 1.55 & -1.15 & -0.12 & 0.72* & .17\\
Item43 & 1.59 & 1.23 & 1.59 & 1.70 & 0.69* & .22\\
Item44 & 3.46 & 1.41 & -0.92 & -0.01 & 0.86* & .38\\
Item45 & 2.04 & 1.66 & 0.46 & -1.12 & 0.87* & .29\\
Item46 & 1.57 & 1.40 & 0.97 & -0.07 & 0.82* & .38\\
Item47 & 2.07 & 1.23 & 0.59 & -0.42 & 0.89* & .34\\
Item48 & 2.57 & 1.30 & 0.14 & -0.74 & 0.93* & .31\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1} \caption{Correlation plot of the items}\label{fig:figCorAppB}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/facIdFigAppB-1.pdf}
\caption{\label{fig:facIdFigAppB}Factor Identification (A) Parallel analysis
(B) Scree Plot}
\end{figure}

@@

\begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}\\
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:EFATableAppB} continued}}\\
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
\endhead
item19 & 0.99 &  &  &  &  & 1.007 & -0.007 & 1.058\\
item20 & 0.91 &  &  &  &  & 0.874 & 0.126 & 1.114\\
item18 & 0.82 &  &  &  &  & 0.711 & 0.289 & 1.123\\
item21 & 0.8 &  &  &  &  & 0.683 & 0.317 & 1.163\\
item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.298\\
item11 &  & 0.83 &  &  &  & 0.687 & 0.313 & 1.007\\
item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.031\\
item12 &  & 0.56 &  &  &  & 0.371 & 0.629 & 1.374\\
item8 &  & -0.44 &  &  &  & 0.206 & 0.794 & 1.106\\
item7 &  & 0.42 &  &  &  & 0.226 & 0.774 & 1.614\\
item9 &  & 0.33 &  &  &  & 0.115 & 0.885 & 1.1\\
item16 &  &  & 0.95 &  &  & 0.946 & 0.054 & 1.097\\
item17 &  &  & 0.74 &  &  & 0.595 & 0.405 & 1.168\\
item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347 & 1.431\\
item3 &  &  &  & 0.85 &  & 0.746 & 0.254 & 1.048\\
item27 &  &  &  & 0.78 &  & 0.624 & 0.376 & 1.028\\
item40 &  &  &  & 0.71 &  & 0.512 & 0.488 & 1.05\\
item35 &  &  &  &  & 0.58 & 0.351 & 0.649 & 1.091\\
item48 &  &  &  &  & 0.57 & 0.354 & 0.646 & 1.144\\
item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.085\\
item47 &  &  &  &  & 0.52 & 0.294 & 0.706 & 1.186\\
item44 &  &  &  &  & 0.45 & 0.216 & 0.784 & 1.145\\
item31 &  &  &  &  & 0.41 & 0.206 & 0.794 & 1.477\\
item38 &  &  &  &  & 0.33 & 0.129 & 0.871 & 1.317\\
\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  &  & \\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1.pdf}
\caption{\label{fig:EFAResidualsAppB} Histogram of residulas: five-factor
solution}
\end{figure}
\end{appendix}
